Convective penetration probably parameterizes convective overshoot

### 2021-07-19 manuscript/ms.tex
Update ms.tex
Abstract

\begin{abstract}
Most stars host convection zones in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we examine how convective motions efficiently mix entropy in the radiative zone.
We present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
We conduct 3D simulations with Dedalus using a simplified Boussinesq model of stellar convection including a radiative flux, and we find good agreement between simulations and the derived theory.
We evolve these simulations for thousands of overturn times; over these long timescales our simulations consistently develop large penetrative regions.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
We discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}

>>>>

\begin{abstract}
Most stars host convection zones in which heat is transported directly by fluid motion.
Parameterizations like mixing length theory adequately describe convective flows in the bulk of these regions, but the behavior of convective boundaries is not well understood.
Here we present 3D numerical simulations which exhibit penetration zones: regions where the entire luminosity \emph{could} be carried by radiation, but where the temperature gradient is approximately adiabatic and convection is present.
To parameterize this effect, we define the ``penetration parameter'' $\mP$ which compares how far the radiative gradient deviates from the adiabatic gradient on either side of the Schwarzschild convective boundary.
Following \citet{roxburgh1989} and \citet{zahn1991}, we construct an energy-based model in which the extent of penetration is controlled by $\mP$.
We compare this theory to 3D numerical simulations using a simplified Boussinesq model of stellar convection.
Although it can take thousands of overturn times to develop, in all cases we find significant convective penetration.
In stellar contexts, we expect $\mathcal{P} \approx 1$ and in this regime our results suggest that convection zones may extend beyond the Schwarzschild boundary by up to $\sim$20-30\% of a mixing length.
We present a MESA solar model which employs our parameterization of convective penetration, and find that the base of the solar convection zone extends by $\sim$35\% of a pressure scale height.
We discuss prospects for extending these results to more realistic stellar contexts.
\end{abstract}
\keywords{UAT keywords}
